\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

In this work, we study the emergence of such spatio-temporal spiking motifs when training a single layer of spiking neurons on a supervised classification task (\seeFig{motionclouds}). We develop a SNN-like method able to learn hetero-synaptic delays to perform motion detection on a synthetic event-based dataset. Because neuromorphic devices are, by design, good candidates to integrate computations with time, we highlight the fact that this event-driven algorithm is transferable to such hardware.
%
\section{Methods}
\label{sec:methods}
%
%
% We expect our model to be able to efficiently detect temporal patterns. Here, we will challenge it by defining a realistic task of motion detection in a stream generated by a natural scene with known ground truth motion. This ground truth will be used to learn the weights and delays of the network in a supervised fashion.
%
Our SNN model will be tested on an appropriate computational task of detecting motion in an event-based sensory input. By analogy with biological requirements, we will design a paradigm simulating eye movements where an input image is moved by a parameterized saccadic trajectory. The task is then to guess the movement as accurately as possible (see fig: movement - task). This is, for example, useful in real life situations to compensate for this motion and provide a motion invariant image categorization by stabilizing the image on the retina.
%
\subsection{Task definition: fast motion detection}
%
%Taking analogy with biological conditions, a common use case for motion detection is to estimate the motion generated on a sensor by saccade-like movements. Saccades are rapid movements of the eyeball which allow to reposition the axis of view in a short period. In humans, these are particularly rapid 
%To test our model, we will quantify its ability to categorize different motions. In that order, we will generate a natural

Let's first define a biologically inspired trajectory inspired by eye movements. Indeed, these allow to dynamically actuate the axis of vision in the visual field of view. For instance, Saccades are rapid movements of the eyeball which reposition the center of vision. In humans, these are Very frequent (on average every 3 seconds [ ]). They are produced very rapidly C- 80ms) and the peak speed is proportional to the amplitude of the displacement (up to 600 deg/sec for a large saccade of 30deg of amplitude). At a more microscopic scale, the gaze moves with are incessant drift similar to a Brownian-like trajectory (Poletti 2015). To keep with the generality of the task, we defined eye movements using a form of Random walk (Engbert 211). This consists first to define a finite set of
possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set motion set of eye motions as the cartesian product of N-V-phi=8 linearly spaced motion directions and N-Y-speed=7 different speeds (see inset of fig : motion - task, a). Note that speeds are sampled on a geometric scale between $1/4$ and $v-speed_base = 4$. Second, we define the trajectory as segments whose duration are drawn from a Poisson distribution with an average length of block-length = 20 ms - similar to a Levy flight. Finally, the trajectory is integrated by assuming 1/that speeds are uniformly and independently sampled from the set of different motions motion-set and 2/ that motion is uniform during a time segment. resulting instances are giving qualitatively similar trajectories as those observed for eye movements as observed for instance in humans (see figure fig : motion-task - a) .

>>>>

In this work, we study the emergence of such spatio-temporal spiking motifs when training a single layer of spiking neurons on a supervised classification task (\seeFig{motionclouds}). We develop a SNN-like method able to learn hetero-synaptic delays to perform motion detection on a synthetic event-based dataset. Because neuromorphic devices are, by design, good candidates to integrate computations with time, we highlight the fact that this event-driven algorithm is transferable to such hardware.
%
\section{Methods}
\label{sec:methods}
%
%
% We expect our model to be able to efficiently detect temporal patterns. Here, we will challenge it by defining a realistic task of motion detection in a stream generated by a natural scene with known ground truth motion. This ground truth will be used to learn the weights and delays of the network in a supervised fashion.
%
Our SNN model will be tested on an appropriate computational task of detecting motion in an event-based sensory input. By analogy with biological requirements, we will design a paradigm simulating eye movements where an input image is moved by a parameterized saccadic trajectory. The task is then to guess the movement as accurately as possible (see fig: movement - task). This is, for example, useful in real life situations to compensate for this motion and provide a motion invariant image categorization by stabilizing the image on the retina.
%
\subsection{Task definition: fast motion detection}
%
%Taking analogy with biological conditions, a common use case for motion detection is to estimate the motion generated on a sensor by saccade-like movements. Saccades are rapid movements of the eyeball which allow to reposition the axis of view in a short period. In humans, these are particularly rapid 
%To test our model, we will quantify its ability to categorize different motions. In that order, we will generate a natural
Let us first define a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision in the field of vision. For example, saccades are rapid movements of the eyeball that reposition the center of vision towards points of interest. In humans, these are very frequent (on average every 3 seconds [ ]). They are produced very rapidly (about 80ms) and the maximum speed is proportional to the amplitude of the displacement (up to 600 deg/sec for a large saccade of 30deg amplitude). At a more microscopic scale, the gaze moves with an incessant drift similar to a Brownian-like trajectory (Poletti 2015). To maintain the full generality of the task, we defined eye movements using a form of random walk (Engbert 211). This approach first defines a defined set of possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of N-V-phi=8 linearly spaced motion directions and N-Y-velocity=7 different velocities (see inset of Fig: motion-task, a). Note that the velocities are sampled on a geometric scale between $1/4$ and $v-speed_base = 4$. Next, we define the trajectory as segments whose duration is drawn from a Poisson distribution with an average block length = 20 ms - similar to a Lévy flight. Finally, the trajectory is integrated by assuming 1/ that velocities are uniformly and independently sampled from the set of different motion-sets and 2/ that motion is uniform during a time segment. The resulting instances yield trajectories qualitatively similar to those observed for eye movements as observed for example in humans (see figure fig: motion-task - a).
